Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-23 doc/paper.Rmd
more crossvalidation

errorsCV %>% 
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv)), size=2.5) +
  geom_line(aes(group=alpha),  size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha),
                      palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate")

@@

cvcs2 %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo))) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~method, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")

>>>>

errorsCV %>% 
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv)), size=2.5) +
  geom_smooth(aes(group=alpha), se=FALSE, method="loess", span=1,  size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha),
                      palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate")

@@

cvcs2 %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo), 
             shape=factor(wv))) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(wv~method, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")
